Solving Collective Spin Hamiltonians with Decoherence

### 2018-09-06 soc_squeezing/cumulant_expansions.tex
added initial conditions for (mu,z,bmu), rather than just (+,z,-) removed redundand sandwich identities changed OAT correlators to incorporate arbitrary single-spin decoherence

The case of the one-axis twisting is simplest to consider, as we can
write the Hamiltonian in the form
\begin{align}
  H_{\t{OAT}} = \f14 \chi \sum_{j,k} \sigma_\z^{(j)} \sigma_\z^{(k)}
  = \f12 \chi \sum_{j<k} \sigma_\z^{(j)} \sigma_\z^{(k)} + \f14 N \chi,
\end{align}
which admits an exact solution previously worked out by Foss-Feig et
al.~in ref.~\cite{foss-feig2013nonequilibrium}.  Adapting exact
expectation values with respect to the initial state $\ket{\X}$
satisfying $S_\x\ket{\X}=S\ket{\X}$, in terms of
$\mu,\nu\in\set{+1,-1}$ we find that
\begin{align}
  \bk{S_+}
  &= \sum_j\bk{\sigma_+^{(j)}}
  = \f{N}{2} e^{-\gamma t/2} \Phi\p{\chi,t}^{N-1}, \label{eq:S+_OAT} \\
  \bk{S_\mu S_\z}
  &= \f12\sum_j\bk{\sigma_\mu^{(j)}\sigma_\z^{(j)}}
  + \f12\sum_{j\ne k} \bk{\sigma_\mu^{(j)} \sigma_\z^{(k)}} \\
  &= -\f{\mu}{2}\bk{S_\mu} + \f14 N \p{N-1} e^{-\gamma t/2}
  \Psi\p{\mu\chi,t} \Phi\p{\chi,t}^{N-2}, \\
  \bk{S_\mu S_\nu}
  &= \sum_j \bk{\sigma_\mu^{(j)} \sigma_\nu^{(j)}}
  + \sum_{j\ne k} \bk{\sigma_\mu^{(j)} \sigma_\nu^{(k)}} \\
  &= \delta_{\mu,-\nu} \p{\f{N}{2} + \mu \bk{S_\z}}
  + \f14 N \p{N-1} e^{-\gamma t}
  \Phi\p{\sp{\mu+\nu}\chi,t}^{N-2}, \label{eq:SS+-_OAT}
\end{align}
where
\begin{align}
  \Phi\p{\zeta,t} \equiv e^{-\gamma t/2}
  \sp{\cos\p{s_\zeta t}+\f12\gamma t~\t{sinc}\p{s_\zeta t}},
  &&
  \Psi\p{\zeta,t} \equiv e^{-\gamma t/2}
  \p{is_\zeta-\gamma/2}t~ \t{sinc}\p{s_\zeta t},
\end{align}
and $s_\zeta \equiv \zeta + i2\gamma$.  The last ingredients we need
to compute spin squeezing at any time are $\bk{S_\z}$ and
$\bk{S_\z^2}$.  As these operators commute with the OAT Hamiltonian,
their evolution is governed entirely by decoherence through
uncorrelated decay of individual spins, which means (see Appendix
\ref{sec:decay_single})
\begin{align}
  \f{d}{dt} S_\z = -\gamma \p{S + S_\z},
  &&
  \f{d}{dt}\p{S_\z^2} = \gamma \p{S + S_\z} \p{1 - 2S_\z},
\end{align}
where $S\equiv N/2$.  The initial conditions $\bk{S_\z}_{t=0}=0$ and
$\bk{S_\z^2}_{t=0}=S/2$ then imply
\begin{align}
  \bk{S_\z} = S\p{e^{-\gamma t}-1},
  &&
  \bk{S_\z^2} = S \p{1 - \f12 e^{-\gamma t}} e^{-\gamma t} + \bk{S_\z}^2.
  \label{eq:Sz_OAT}
\end{align}
The expectation values in \eqref{eq:S+_OAT}-\eqref{eq:SS+-_OAT} and
\eqref{eq:Sz_OAT} are sufficient to compute the squeezing parameter
$\xi^2$ defined in \eqref{eq:squeezing} at any time throughout
evolution of the initial state $\ket{\X}:S_\x\ket{\X}=S\ket{\X}$ under
$H_{\t{OAT}}$.

\section{Truncated Heisenberg operator dynamics}

@@

@@

We first compute sums of single-spin operators sandwiching $S_\z^m$,
which will in turn be used to compute similar sums sandwiching
$S_\mu^\ell S_\z^m S_\bmu^n$.  The simplest case is
  \sum_j \sigma_\z^{(j)} S_\z^m \sigma_\z^{(j)}
  = \sum_j \sigma_\z^{(j)} \sigma_\z^{(j)} S_\z^m
  = \sum_j \1_j S_\z^m
  = 2 S S_\z^m.
Similarly,
  \sum_j \sigma_\z^{(j)} S_\z^m \sigma_\mu^{(j)}
  = S_\z^m \sum_j \sigma_\z^{(j)} \sigma_\mu^{(j)}
  = S_\z^m \sum_j \mu \sigma_\mu^{(j)}
  = \mu S_\z^m S_\mu
  = \mu S_\mu \p{\mu+S_\z}^m,
where in the last equality we used the identity derived in
\eqref{eq:push_z_mu_single} to push $S_\mu$ through $S_\z^m$.  Using
identity \eqref{eq:push_z_mu_Ss} to push $\sigma_\mu^{(j)}$ through
$S_\z^m$, we can also find
  \sum_j \sigma_\mu^{(j)} S_\z^m \sigma_\mu^{(j)}
  = \sum_j \sigma_\mu^{(j)} \sigma_\mu^{(j)} \p{\mu+S_\z}^m
  = 0,
  \sum_j \sigma_\bmu^{(j)} S_\z^m \sigma_\mu^{(j)}
  = \sum_j \sigma_\bmu^{(j)} \sigma_\mu^{(j)} \p{\mu+S_\z}^m
  = \p{S-\mu S_\z} \p{\mu+S_\z}^m.
We are now equipped to derive similar identities for general ordered
products of collective spin operators.  For quick reference, we
provide here identity \eqref{eq:push_z_mu_sS} and its conjugate:
  \sigma_\z^{(j)} S_\mu^\ell
  = S_\mu^\ell \sigma_\z^{(j)} + 2\mu \ell S_\mu^{\ell-1}\sigma_\mu^{(j)},
  S_\bmu^n \sigma_\z^{(j)}
  = \sigma_\z^{(j)} S_\bmu^n + 2\mu n \sigma_\bmu^{(j)} S_\bmu^{n-1},
and likewise with identity \eqref{eq:push_mu_Ss}:
  \sigma_\bmu^{(j)} S_\mu^\ell
  &= S_\mu^\ell \sigma_\bmu^{(j)}
  - \ell \p{\ell-1} S_\mu^{\ell-2} \sigma_\mu^{(j)}
  - \mu \ell S_\mu^{\ell-1} \sigma_\z^{(j)}, \\
  S_\bmu^n \sigma_\mu^{(j)}
  &= \sigma_\mu^{(j)} S_\bmu^n
  - n \p{n-1} \sigma_\bmu^{(j)} S_\bmu^{n-2}
  - \mu n \sigma_\z^{(j)} S_\bmu^{n-1}.
Working through the combinations, we then compute
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\bmu^{(j)}
  &= S_\mu^\ell \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n,
  \label{eq:sand_mu_bmu} \allowdisplaybreaks \\
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\z^{(j)}
  &= -\mu S_\mu^{\ell+1} S_\z^m S_\bmu^n
  + 2\mu n S_\mu^\ell \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-1},
  \allowdisplaybreaks \\
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\bmu^{(j)}
  &= -\mu S_\mu^\ell S_\z^m S_\bmu^{n+1}
  + 2\mu \ell S_\mu^{\ell-1} \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n,
  \allowdisplaybreaks \\
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\z^{(j)}
  &= 2\p{S-\ell-n} S_\mu^\ell S_\z^m S_\bmu^n
  + 4\ell n S_\mu^{\ell-1} \p{S+\mu S_\z}
  \p{-\mu+S_\z}^m S_\bmu^{n-1},
  \label{eq:sand_z_z} \allowdisplaybreaks \\
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= -n\p{n-1} S_\mu^\ell \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2}
  + n S_\mu^{\ell+1} S_\z^m S_\bmu^{n-1},
  \allowdisplaybreaks \\
  \sum_j \sigma_\bmu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\bmu^{(j)}
  &= -\ell \p{\ell-1} S_\mu^{\ell-2}
  \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^n
  + \ell S_\mu^{\ell-1} S_\z^m S_\bmu^{n+1},
  \allowdisplaybreaks \\
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= \mu S_\mu^{\ell+1} \p{\mu+S_\z}^m S_\bmu^n
  + \mu n \p{-2S+2\ell+n-1} S_\mu^\ell S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad - 2\mu\ell n\p{n-1} S_\mu^{\ell-1}
  \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2},
  \allowdisplaybreaks \\
  \sum_j \sigma_\bmu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\z^{(j)}
  &= \mu S_\mu^\ell \p{\mu+S_\z}^m S_\bmu^{n+1}
  + \mu \ell \p{-2S+2n+\ell-1} S_\mu^{\ell-1} S_\z^m S_\bmu^n \notag \\
  &\qquad - 2\mu\ell n\p{\ell-1} S_\mu^{\ell-2}
  \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-1},
  \allowdisplaybreaks \\
  \sum_j \sigma_\bmu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= S_\mu^\ell \p{S - \ell - n - \mu S_\z} \p{\mu + S_\z}^m S_\bmu^n
  + \ell n \p{2S - \ell - n + 2}
  S_\mu^{\ell-1} S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad + \ell n \p{\ell-1} \p{n-1} S_\mu^{\ell-2} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-2}.
  \label{eq:sand_bmu_mu}

@@

@@

The effect of decoherence via uncorrelated decay ($\mu=-1$) or
excitation ($\mu=1$) of individual spins is described by (with
$\bmu\equiv-\mu$),
\begin{align}
  \D\p{\sigma_\mu; \O}
  = \sum_j\p{\sigma_\bmu^{(j)} \O \sigma_\mu^{(j)}
    - \f12\sp{\sigma_\bmu^{(j)} \sigma_\mu^{(j)},\O}_+}
  = \sum_j \sigma_\bmu^{(j)} \O \sigma_\mu^{(j)}
    - S \O + \f{\mu}{2} \sp{S_\z, \O}_+.
\end{align}
In order to determine the effect of this decoherence on ordered
products of collective spin operators, we expand the anti-commutator
\begin{align}
  \sp{S_\z, S_\mu^\ell S_\z^m S_\bmu^n}_+
  = S_\z S_\mu^\ell S_\z^m S_\bmu^n + S_\mu^\ell S_\z^m S_\bmu^n S_\z
  = S_\mu^\ell\p{\mu\ell + \mu n + 2 S_\z} S_\z^m S_\bmu^n,
\end{align}
which implies, using \eqref{eq:sand_mu_bmu},
\begin{align}
  \D\p{\sigma_\bmu; S_\mu^\ell S_\z^m S_\bmu^n}
  &= S_\mu^\ell \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n
  - S_\mu^\ell\p{S + \f12\sp{\ell+n} + \mu S_\z} S_\z^m S_\bmu^n \\
  &= S_\mu^\ell \sp{\p{S+\mu S_\z}
    \sum_{k=0}^{m-1} \p{-\mu}^{m-k} { m \choose k } S_\z^k
    - \f12 \p{\ell+n} S_\z^m} S_\bmu^n,
  \label{eq:decay_diff}
\end{align}
and, using \eqref{eq:sand_bmu_mu},
\begin{align}
  \D\p{\sigma_\mu; S_\mu^\ell S_\z^m S_\bmu^n}
  &= S_\mu^\ell \p{S - \ell - n - \mu S_\z} \p{\mu + S_\z}^m S_\bmu^n
  + \ell n \p{2S - \ell - n + 2}
  S_\mu^{\ell-1} S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad + \ell n \p{\ell-1} \p{n-1} S_\mu^{\ell-2} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-2} \notag \\
  &\qquad - S_\mu^\ell\p{S - \f12\sp{\ell+n} - \mu S_\z}
  S_\z^m S_\bmu^n \allowdisplaybreaks \\
  &= S_\mu^\ell \sp{\p{S-\ell-n-\mu S_\z}
    \sum_{k=0}^{m-1} \mu^{m-k} { m \choose k } S_\z^k
    - \f12 \p{\ell+n} S_\z^m} S_\bmu^n \notag \\
  &\qquad + \ell n \p{2S - \ell - n + 2}
  S_\mu^{\ell-1} S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad + \ell n \p{\ell-1} \p{n-1} S_\mu^{\ell-2} \p{S + \mu S_\z}
  \sum_{k=0}^m \p{-\mu}^{m-k} { m \choose k } S_\z^k S_\bmu^{n-2}.
  \label{eq:decay_same}
\end{align}
Decoherence via jump operators $\sigma_\bmu^{(j)}$ only couples
operators $S_\mu^\ell S_\z^m S_\bmu^n$ to operators
$S_\mu^\ell S_\z^{m'} S_\bmu^n$ with $m'\le m$.  Decoherence via jump
operators $\sigma_\mu^{(j)}$, meanwhile, makes operators
$S_\mu^\ell S_\z^m S_\bmu^n$ ``grow'' in $S_\z$ through the last term
in \eqref{eq:decay_same} with $k=m$, although the sum $\ell+m+n$ does
not grow.

The effect of decoherence via single-spin dephasing is described by
\begin{align}
  \D\p{\sigma_\z/\sqrt2; \O}
  = \sum_j\p{\sigma_\z^{(j)} \O \sigma_\z^{(j)}
    - \f12\sp{\sigma_\z^{(j)} \sigma_\z^{(j)},\O}_+}
  = \f12 \sum_j \sigma_\z^{(j)} \O \sigma_\z^{(j)} - S \O,
\end{align}
where the factor $\sqrt2$ is inserted as
e.g.~$\D\p{\sigma_\z/\sqrt2;S_\x}=-S_\x$.  From \eqref{eq:sand_z_z},
we then have
\begin{align}
  \D\p{\sigma_\z/\sqrt2; S_\mu^\ell S_\z^m S_\bmu^n}
  &= -\p{\ell+n} S_\mu^\ell S_\z^m S_\bmu^n
  + 2 \ell n S_\mu^{\ell-1} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-1} \\
  &= -\p{\ell+n} S_\mu^\ell S_\z^m S_\bmu^n
  + 2 \ell n S_\mu^{\ell-1} \p{S + \mu S_\z}
  \sum_{k=0}^m \p{-\mu}^{m-k} { m \choose k } S_\z^k S_\bmu^{n-1}.
\end{align}
Decoherence via single-spin dephasing also makes operators
$S_\mu^\ell S_\z^m S_\bmu^n$ ``grow'' in $S_\z$, although the sum
$\ell+m+n$ still does not grow.

>>>>

The case of the one-axis twisting is simplest to consider, as we can
write the Hamiltonian in the form
\begin{align}
  H_{\t{OAT}} = \f14 \chi \sum_{j,k} \sigma_\z^{(j)} \sigma_\z^{(k)}
  = \f12 \chi \sum_{j<k} \sigma_\z^{(j)} \sigma_\z^{(k)} + \f14 N \chi,
\end{align}
which admits an exact solution previously worked out by Foss-Feig et
al.~in ref.~\cite{foss-feig2013nonequilibrium}.  Adapting exact
expectation values with respect to the initial state $\ket{\X}$
satisfying $S_\x\ket{\X}=S\ket{\X}$, in terms of $S\equiv N/2$ and
$\mu,\nu\in\set{+1,-1}$ we find that
\begin{align}
  \bk{S_+}
  &= \sum_j\bk{\sigma_+^{(j)}}
  = S e^{-\Gamma t} \Phi\p{\chi,t}^{N-1}, \label{eq:S+_OAT} \\
  \bk{S_\mu S_\z}
  &= \f12\sum_j\bk{\sigma_\mu^{(j)}\sigma_\z^{(j)}}
  + \f12\sum_{j\ne k} \bk{\sigma_\mu^{(j)} \sigma_\z^{(k)}} \\
  &= -\f{\mu}{2}\bk{S_\mu} + S \p{S-\f12} e^{-\Gamma t}
  \Psi\p{\mu\chi,t} \Phi\p{\chi,t}^{N-2}, \\
  \bk{S_\mu S_\nu}
  &= \sum_j \bk{\sigma_\mu^{(j)} \sigma_\nu^{(j)}}
  + \sum_{j\ne k} \bk{\sigma_\mu^{(j)} \sigma_\nu^{(k)}} \\
  &= \delta_{\mu,-\nu} \p{S + \mu\bk{S_\z}}
  + S \p{S-\f12} e^{-2\Gamma t}
  \Phi\p{\sp{\mu+\nu}\chi,t}^{N-2}, \label{eq:SS+-_OAT}
\end{align}
where
\begin{align}
  \Phi\p{\zeta,t}
  &\equiv e^{-\lambda t} \sp{\cos\p{t\sqrt{s_\zeta^2-r}}
    + \lambda t~\t{sinc}\p{t\sqrt{s_\zeta^2-r}}},
  \\
  \Psi\p{\zeta,t}
  &\equiv e^{-\lambda t} \p{is_\zeta-\gamma}t~
  \t{sinc}\p{t\sqrt{s_\zeta^2-r}},
\end{align}
for
\begin{align}
  \gamma \equiv \f12 \p{\gamma_+ - \gamma_-},
  &&
  \lambda \equiv \f12 \p{\gamma_+ + \gamma_-},
  &&
  r \equiv \gamma_+ \gamma_-,
  &
  \Gamma \equiv \gamma_z + \lambda,
  &&
  s_\zeta \equiv \zeta + i\gamma,
\end{align}
defined respectively in terms of spontaneous uncorrelated spin
dephasing, excitation, and decay rates $\gamma_z$, $\gamma_+$,
$\gamma_-$.  The last ingredients we need to compute spin squeezing at
any time are $\bk{S_\z}$ and $\bk{S_\z^2}$.  As these operators
commute with the OAT Hamiltonian, their evolution is governed entirely
by decoherence (see Appendix \ref{sec:decay_single}), which means
\begin{align}
  \f{d}{dt} S_\z
  &= S\p{\gamma_+-\gamma_-} - \p{\gamma_++\gamma_-} S_\z,
  \\
  \f{d}{dt}\p{S_\z^2}
  &= S\p{\gamma_++\gamma_-} + 2\p{\gamma_+-\gamma_-}\p{S-\f12} S_\z
  - 2 \p{\gamma_++\gamma_-} S_\z^2.
\end{align}
The initial conditions $\bk{S_\z}_{t=0}=0$ and $\bk{S_\z^2}_{t=0}=S/2$
then imply
\begin{align}
  \bk{S_\z}
  = S\p{\f{\gamma_+-\gamma_-}{\gamma_++\gamma_-}}
  \p{1-e^{-\p{\gamma_+ + \gamma_-} t}},
  &&
  \bk{S_\z^2} = S \sp{\f12 + \p{S-\f12} \f{\bk{S_z}^2}{S^2}}.
  \label{eq:Sz_OAT}
\end{align}
The expectation values in \eqref{eq:S+_OAT}-\eqref{eq:SS+-_OAT} and
\eqref{eq:Sz_OAT} are sufficient to compute the squeezing parameter
$\xi^2$ defined in \eqref{eq:squeezing} at any time throughout
evolution of the initial state $\ket{\X}:S_\x\ket{\X}=S\ket{\X}$ under
$H_{\t{OAT}}$.

\section{Truncated operator dynamics}

@@

\section{One-axis twisting revisited}

@@

We first compute sums of single-spin operators sandwiching $S_\z^m$,
which will in turn be used to compute similar sums sandwiching
$S_\mu^\ell S_\z^m S_\bmu^n$.  The simplest case is
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\z^m \sigma_\z^{(j)}
  = \sum_j \sigma_\z^{(j)} \sigma_\z^{(j)} S_\z^m
  = \sum_j \1_j S_\z^m
  = 2 S S_\z^m.
\end{align}
Similarly,
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\z^m \sigma_\mu^{(j)}
  = S_\z^m \sum_j \sigma_\z^{(j)} \sigma_\mu^{(j)}
  = S_\z^m \sum_j \mu \sigma_\mu^{(j)}
  = \mu S_\z^m S_\mu
  = \mu S_\mu \p{\mu+S_\z}^m,
\end{align}
where in the last equality we used the identity derived in
\eqref{eq:push_z_mu_single} to push $S_\mu$ through $S_\z^m$.  Using
identity \eqref{eq:push_z_mu_Ss} to push $\sigma_\mu^{(j)}$ through
$S_\z^m$, we can also find
\begin{align}
  \sum_j \sigma_\mu^{(j)} S_\z^m \sigma_\mu^{(j)}
  = \sum_j \sigma_\mu^{(j)} \sigma_\mu^{(j)} \p{\mu+S_\z}^m
  = 0,
\end{align}
and
\begin{align}
  \sum_j \sigma_\bmu^{(j)} S_\z^m \sigma_\mu^{(j)}
  = \sum_j \sigma_\bmu^{(j)} \sigma_\mu^{(j)} \p{\mu+S_\z}^m
  = \p{S-\mu S_\z} \p{\mu+S_\z}^m.
\end{align}
We are now equipped to derive similar identities for general ordered
products of collective spin operators.  For quick reference, we
provide here identity \eqref{eq:push_z_mu_sS} and its conjugate:
\begin{align}
  \sigma_\z^{(j)} S_\mu^\ell
  = S_\mu^\ell \sigma_\z^{(j)} + 2\mu \ell S_\mu^{\ell-1}\sigma_\mu^{(j)},
  &&
  S_\bmu^n \sigma_\z^{(j)}
  = \sigma_\z^{(j)} S_\bmu^n + 2\mu n \sigma_\bmu^{(j)} S_\bmu^{n-1},
\end{align}
and likewise with identity \eqref{eq:push_mu_Ss}:
\begin{align}
  \sigma_\bmu^{(j)} S_\mu^\ell
  &= S_\mu^\ell \sigma_\bmu^{(j)}
  - \ell \p{\ell-1} S_\mu^{\ell-2} \sigma_\mu^{(j)}
  - \mu \ell S_\mu^{\ell-1} \sigma_\z^{(j)}, \\
  S_\bmu^n \sigma_\mu^{(j)}
  &= \sigma_\mu^{(j)} S_\bmu^n
  - n \p{n-1} \sigma_\bmu^{(j)} S_\bmu^{n-2}
  - \mu n \sigma_\z^{(j)} S_\bmu^{n-1}.
\end{align}
Working through all combinations that are unique up to conjugation, we
then compute
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\z^{(j)}
  &= 2\p{S-\ell-n} S_\mu^\ell S_\z^m S_\bmu^n
  + 4\ell n S_\mu^{\ell-1} \p{S+\mu S_\z}
  \p{-\mu+S_\z}^m S_\bmu^{n-1},
  \label{eq:sand_z_z} \allowdisplaybreaks \\
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= \mu S_\mu^{\ell+1} \p{\mu+S_\z}^m S_\bmu^n
  + \mu n \p{-2S+2\ell+n-1} S_\mu^\ell S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad - 2\mu\ell n\p{n-1} S_\mu^{\ell-1}
  \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2},
  \label{eq:sand_z_mu} \allowdisplaybreaks \\
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\bmu^{(j)}
  &= -\mu S_\mu^\ell S_\z^m S_\bmu^{n+1}
  + 2\mu \ell S_\mu^{\ell-1} \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n,
  \label{eq:sand_z_bmu} \allowdisplaybreaks \\
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= -n\p{n-1} S_\mu^\ell \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2}
  + n S_\mu^{\ell+1} S_\z^m S_\bmu^{n-1},
  \label{eq:sand_mu_mu} \allowdisplaybreaks \\
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\bmu^{(j)}
  &= S_\mu^\ell \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n,
  \label{eq:sand_mu_bmu} \allowdisplaybreaks \\
  \sum_j \sigma_\bmu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= S_\mu^\ell \p{S - \ell - n - \mu S_\z} \p{\mu + S_\z}^m S_\bmu^n
  + \ell n \p{2S - \ell - n + 2}
  S_\mu^{\ell-1} S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad + \ell n \p{\ell-1} \p{n-1} S_\mu^{\ell-2} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-2}.
  \label{eq:sand_bmu_mu}
\end{align}

@@

The effect of decoherence via single-spin dephasing is described by
\begin{align}
  \D\p{\sigma_\z/\sqrt2; \O}
  = \sum_j\p{\sigma_\z^{(j)} \O \sigma_\z^{(j)}
    - \f12\sp{\sigma_\z^{(j)} \sigma_\z^{(j)},\O}_+}
  = \f12 \sum_j \sigma_\z^{(j)} \O \sigma_\z^{(j)} - S \O,
\end{align}
where the factor $\sqrt2$ is inserted as
e.g.~$\D\p{\sigma_\z/\sqrt2;S_\x}=-S_\x$.  From \eqref{eq:sand_z_z},
we then have
\begin{align}
  \D\p{\sigma_\z/\sqrt2; S_\mu^\ell S_\z^m S_\bmu^n}
  = -\p{\ell+n} S_\mu^\ell S_\z^m S_\bmu^n
  + 2 \ell n S_\mu^{\ell-1} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-1}.
\end{align}
Decoherence via single-spin dephasing makes operators
$S_\mu^\ell S_\z^m S_\bmu^n$ ``grow'' in $S_\z$, although the sum
$\ell+m+n$ does not grow.

@@

The effect of decoherence via uncorrelated decay ($\mu=-1$) or
excitation ($\mu=1$) of individual spins is described by (with
$\bmu\equiv-\mu$),
\begin{align}
  \D\p{\sigma_\mu; \O}
  = \sum_j\p{\sigma_\bmu^{(j)} \O \sigma_\mu^{(j)}
    - \f12\sp{\sigma_\bmu^{(j)} \sigma_\mu^{(j)},\O}_+}
  = \sum_j \sigma_\bmu^{(j)} \O \sigma_\mu^{(j)}
    - S \O + \f{\mu}{2} \sp{S_\z, \O}_+.
\end{align}
In order to determine the effect of this decoherence on ordered
products of collective spin operators, we expand the anti-commutator
\begin{align}
  \sp{S_\z, S_\mu^\ell S_\z^m S_\bmu^n}_+
  = S_\z S_\mu^\ell S_\z^m S_\bmu^n + S_\mu^\ell S_\z^m S_\bmu^n S_\z
  = S_\mu^\ell\p{\mu\ell + \mu n + 2 S_\z} S_\z^m S_\bmu^n,
\end{align}
which implies, using \eqref{eq:sand_mu_bmu},
\begin{align}
  \D\p{\sigma_\bmu; S_\mu^\ell S_\z^m S_\bmu^n}
  = S_\mu^\ell \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n
  - S_\mu^\ell\p{S + \f12\sp{\ell+n} + \mu S_\z} S_\z^m S_\bmu^n,
  \label{eq:decay_diff}
\end{align}
and, using \eqref{eq:sand_bmu_mu},
\begin{align}
  \D\p{\sigma_\mu; S_\mu^\ell S_\z^m S_\bmu^n}
  &= S_\mu^\ell \p{S - \ell - n - \mu S_\z} \p{\mu + S_\z}^m S_\bmu^n
  - S_\mu^\ell\p{S - \f12\sp{\ell+n} - \mu S_\z}
  S_\z^m S_\bmu^n \notag \\
  &\qquad + \ell n \p{2S - \ell - n + 2}
  S_\mu^{\ell-1} S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad + \ell n \p{\ell-1} \p{n-1} S_\mu^{\ell-2} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-2}.
  \label{eq:decay_same}
\end{align}
Decoherence via jump operators $\sigma_\bmu^{(j)}$ only couples
operators $S_\mu^\ell S_\z^m S_\bmu^n$ to operators
$S_\mu^\ell S_\z^{m'} S_\bmu^n$ with $m'\le m$.  Decoherence via jump
operators $\sigma_\mu^{(j)}$, meanwhile, makes operators
$S_\mu^\ell S_\z^m S_\bmu^n$ ``grow'' in $S_\z$ through the last term
in \eqref{eq:decay_same} with $k=m$, although the sum $\ell+m+n$ does
not grow.
